### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Created trends in zestimates graph

\begin{tabular}{llcccc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
 &  & Mean & N & Mean & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
 & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
 & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
 & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
 & No cause & 0.12 & 3651 & 0.10 & 10708 \\
 & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
 & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
 & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
 & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
 & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
 & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
 & Case voluntarily dismissed & 0.00 & 3651 & 0.00 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 3651 & 0.07 & 10708 \\
 & Plaintiff has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
 & Defendant is an entity & 0.01 & 3651 & 0.01 & 10708 \\
 & Plaintiff is an entity & 0.62 & 3651 & 0.67 & 10708 \\
 & Money judgment & 63.61 & 3651 & 3688.76 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
 & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
 & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
 & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
 & Units & 41.23 & 1256 & 42.09 & 3992 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 865 & 279947.69 & 2362 \\
 & Four years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
 & Three years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
 & Two years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
 & One year before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
 & Latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
 & One year after latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
 & Two years after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
 & Three years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
\cline{1-6}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llcccc}
\toprule
 &  & \multicolumn{2}{c}{\textit{Cases Won by Defendant}} & \multicolumn{2}{c}{\textit{Cases Won by Plaintiff}} \\
 &  & Mean & N & Mean & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
 & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
 & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
 & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
 & No cause & 0.12 & 3651 & 0.10 & 10708 \\
 & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
 & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
 & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
\cline{1-6}
\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
 & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
 & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
 & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.22 & 3651 & 0.07 & 10708 \\
 & Defendant has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
 & Plaintiff has an attorney & 0.01 & 3651 & 0.01 & 10708 \\
 & Defendant is an entity & 0.62 & 3651 & 0.67 & 10708 \\
 & Plaintiff is an entity & 63.61 & 3651 & 3688.76 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 6478531.48 & 1256 & 8995455.63 & 3992 \\
 & Total property value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
 & Building value & 61247.49 & 1256 & 100993.11 & 3992 \\
 & Land value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
 & Other value & 41.23 & 1256 & 42.09 & 3992 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 252041.76 & 865 & 279947.69 & 2362 \\
 & Five years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
 & Four years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
 & Three years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
 & Two years before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
 & One year before latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
 & Latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
 & One year after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
 & Two years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
\cline{1-6}
\bottomrule
\end{tabular}

### 2022-12-23 output/summary_statistics/tables/summary_statistics.tex
Fixed unrestricted summ stats table bug
Plotted evictions map
Created trends in zestimates graph

\begin{tabular}{llrrr}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{8}{*}{\textit{Panel A: Case Initiation}} & For cause & 0.13 & 0.33 & 30,505 \\
 & For cause (transfer) & 0.01 & 0.09 & 30,505 \\
 & Foreclosure & 0.02 & 0.15 & 30,505 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 30,505 \\
 & No cause & 0.11 & 0.31 & 30,505 \\
 & No cause (transfer) & 0.01 & 0.08 & 30,505 \\
 & Non-payment of rent & 0.71 & 0.46 & 30,505 \\
 & Non-payment of rent (transfer) & 0.02 & 0.13 & 30,505 \\
\cline{1-5}
\multirow[c]{5}{*}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.24 & 0.43 & 30,505 \\
 & Case involuntarily dismissed & 0.12 & 0.33 & 30,505 \\
 & Case heard & 0.07 & 0.26 & 30,505 \\
 & Case mediated & 0.52 & 0.50 & 30,505 \\
 & Case voluntarily dismissed & 0.00 & 0.00 & 30,505 \\
\cline{1-5}
\multirow[c]{5}{*}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.10 & 0.30 & 30,505 \\
 & Plaintiff has an attorney & 0.82 & 0.39 & 30,505 \\
 & Defendant is an entity & 0.01 & 0.08 & 30,505 \\
 & Plaintiff is an entity & 0.66 & 0.47 & 30,505 \\
 & Money judgment & 2405.16 & 5960.84 & 30,505 \\
\cline{1-5}
\multirow[c]{5}{*}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 7731082.50 & 18211631.86 & 12,089 \\
 & Building value & 2007807.90 & 5532224.22 & 12,089 \\
 & Land value & 99020.63 & 539763.97 & 12,089 \\
 & Other value & 9827333.04 & 22977540.22 & 12,089 \\
 & Units & 39.15 & 113.83 & 12,089 \\
\cline{1-5}
\multirow[c]{9}{*}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 263662.99 & 223748.00 & 6,766 \\
 & Four years before latest docket date & 283010.66 & 265189.42 & 6,848 \\
 & Three years before latest docket date & 305906.07 & 337719.48 & 6,950 \\
 & Two years before latest docket date & 344030.70 & 1167207.98 & 6,966 \\
 & One year before latest docket date & 352784.42 & 300314.15 & 6,992 \\
 & Latest docket date & 395691.50 & 416306.93 & 7,045 \\
 & One year after latest docket date & 435193.84 & 476324.79 & 6,943 \\
 & Two years after latest docket date & 474304.25 & 446024.13 & 4,910 \\
 & Three years after latest docket date & 507403.55 & 1140138.35 & 2,680 \\
\cline{1-5}
\bottomrule
\end{tabular}

>>>>

\begin{tabular}{llccc}
\toprule
 &  & Mean & S.D. & N \\
Panel & Variable &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.32 & 37,943 \\
 & For cause (transfer) & 0.01 & 0.08 & 37,943 \\
 & Foreclosure & 0.02 & 0.14 & 37,943 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 37,943 \\
 & No cause & 0.10 & 0.30 & 37,943 \\
 & No cause (transfer) & 0.01 & 0.08 & 37,943 \\
 & Non-payment of rent & 0.74 & 0.44 & 37,943 \\
 & Non-payment of rent (transfer) & 0.02 & 0.13 & 37,943 \\
\cline{1-5}
\multirow[c]{4}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.20 & 0.40 & 37,943 \\
 & Case involuntarily dismissed & 0.30 & 0.46 & 37,943 \\
 & Case heard & 0.06 & 0.24 & 37,943 \\
 & Case mediated & 0.42 & 0.49 & 37,943 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Case voluntarily dismissed & 0.09 & 0.28 & 37,943 \\
 & Defendant has an attorney & 0.84 & 0.37 & 37,943 \\
 & Plaintiff has an attorney & 0.01 & 0.08 & 37,943 \\
 & Defendant is an entity & 0.70 & 0.46 & 37,943 \\
 & Plaintiff is an entity & 1943.41 & 5422.12 & 37,943 \\
\cline{1-5}
\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Money judgment & 9435708.78 & 20612629.31 & 14,491 \\
 & Total property value & 2482603.38 & 6470958.91 & 14,491 \\
 & Building value & 113817.19 & 536568.37 & 14,491 \\
 & Land value & 12020146.88 & 26285935.89 & 14,491 \\
 & Other value & 42.25 & 112.87 & 14,491 \\
\cline{1-5}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Units & 268580.04 & 261642.26 & 8,273 \\
 & Five years before latest docket date & 288822.75 & 298902.01 & 8,384 \\
 & Four years before latest docket date & 311679.90 & 330953.69 & 8,508 \\
 & Three years before latest docket date & 351524.51 & 1127830.09 & 8,524 \\
 & Two years before latest docket date & 358534.63 & 303605.64 & 8,547 \\
 & One year before latest docket date & 402381.22 & 400555.10 & 8,602 \\
 & Latest docket date & 443118.39 & 459237.85 & 8,539 \\
 & One year after latest docket date & 481103.73 & 437176.87 & 5,752 \\
 & Two years after latest docket date & 510339.87 & 1057656.48 & 3,171 \\
\cline{1-5}
\bottomrule
\end{tabular}
